{\bf [25 points] Multiple Sequence Alignment (MSA)}\\
\begin{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item  We discussed in class a method to align two strings using dynamic programming. Consider now the problem of multiple sequence alignment, where more than 2 sequences are simultaneously aligned to each other. The MSA problem is NP-Hard, as is typically approximated using heuristics. One example is the Star MSA method method:\\
To align a given set of strings S:
\begin{itemize}
    \item Build all optimal pairwise alignments
    \item Select the string $S_c$ such that $S_c$ is the most similar to all of the other strings. $S_c$ should minimize $\sum_{i \neq c} a(S_i, S_c)$, where $a(S_i, S_c)$ is the optimal pairwise cost
    \item Align the remaining strings to $S_c$
\end{itemize}
For the following set of strings S, use the Star MSA method to select $S_c$ and write out the optimal alignment of all strings. The scoring parameters are (match $m=2$, mismatch $n=-1$, gap $g=-1$, and gaps that align with each other do not contribute to the score).
\begin{align*}
Seq1& \texttt{  TCGAATC}\\
Seq2& \texttt{  CCCCGAA	}\\
Seq3& \texttt{  TTCGAAC}\\
\end{align*}

\begin{solution}
Add your solution here.
\end{solution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item The selection of $S_c$ will vary based on the scoring parameters. Give new parameters for the mismatch and gap cost such that a new $S_c$ is chosen.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{solution}
Add your solution here.
\end{solution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item A common application of MSA is to find consensus sequences among a set of strings. Provide an additional biological application where multiple sequence alignment would be helpful.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{solution}
Add your solution here.
\end{solution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Report the longest consensus sequence in the set of strings in msa.fa. You can use code to help you.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{solution}
Add your solution here.
\end{solution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{itemize}
